\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
changes

We decided to query only one database, Scopus \cite{c2}, that claims to be the
largest abstract and citation database of peer-reviewed literature.
It indexes the main Computer Science databases : Springer, IEEE, ACM and
others.
The main advantage of using Scopus is that it provides a functionality to
export the result of a search query on its database.
Some of those exported results would not have been easily obtainable on some
publishers search engines that do not provide an export functionality.
Consequently, Scopus was used mostly as a Search and Export portal over the
relevant publications, greatly reducing the effort needed to extract the
original articles set. 
% TODO: Original articles set <- better wording?!
% Pierre "initial articles set " ?

From the two research questions we tried to maximize the number of publications
found on the subject.
% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
% doesn't make any sense.
% Pierre : remplacé par "words with similar meanings"
To achieve that purpose we used for the query a disjunction of synonyms for
\textit{detection} on their respective contracted form : \textit{detect*},
\textit{recogni*} and \textit{ident*}.
We have then added to the query a disjunction of \textit{pattern} and \textit{motif}.
The query was limited to the abstract, the title, and keywords of each article.
% Do we like oxford comma?
% Pierre : je découvre ce que c'est, l'internet semble avoir un avis contreversé, il faut juste rester consistant.

@@

% TODO: This sentence is not necessary... It is evident that we excluded other
% domains.
% Pierre: Difficile à dire vu notre première critère d'exclusion après
We have also limited our research to the field of computer science and
engineering.

The query resulted in a total of 403 articles.
Of those articles, we found two duplicates that were immediately removed from
the set of articles to analyze which brings down the number of articles for
screening to 401.

\begin{figure}
 \centering
  \begin{tabular}{ ccc }
   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
   \hline {}
   1 & 133 & 0.88 \\
   2 & 133 & 0.66 \\
   3 & 134 & 0.91 \\
 \end{tabular}
 \caption{Cohen's Kappa coefficients}
\end{figure}

@@

After having queried the database, we exported the results found and proceeded to screening.

This process was done by pair.
For each article, we check that the result was the same for each individual in
the pair.
In the case of difference, we first talk about it to find common ground, then
if the conflict was not resolved, we asked a senior researcher for a final
decision.

@@

\begin{enumerate}
  \item \textbf{Not a contribution in software engineering}: 
    This criterion was used to exclude articles not relevant to the domain and
    software engineering articles that are nothing more than mere use case
    reports.
  \item \textbf{Not a full conference or research paper},
    This criterion was used to exclude small
  \item \textbf{Not about software design pattern}:
    This criterion excludes articles where the main contribution is not about
    design pattern as defined in by the Gang of Four,
    % TODO: We cannoct base our exclusion to DP defined by the GoF because we
    % have a class for other pattern type.
    % Limiting to software design patterns would be enough
  \item \textbf{The main contribution of the paper is not about a method of detecting design patterns}:
    This criterion was used to exclude benchmarks and other analysis whose main
    purposes are not a method of design pattern detection.
\end{enumerate}

If in article matched more than one criteria, we assigned the lowest criteria
to it.

We were three author to work on the screening, we therefore created three pair
of author including on average 135 articles per pair.

The inter-rater agreement Cohen's kappa gave us the following result presented
in \textit{fig. 1}.

@@

\subsection{Systematic map}

%TODO

@@

@@

\begin{center}
 \begin{figure}
  \includegraphics[scale=0.450]{year_distribution.png}
  \caption{}
 \end{figure}
\end{center}

%\begin{center}
%\includegraphics[scale=0.7]{articles_by_years.png}
%\end{center}

\begin{center}
  \begin{figure}
   \small
   \begin{tabular}{ lll }
    \bf Category & \bf Class & \bf \# of articles \\
    \hline
    \multirow{7}{*}{Detection Strategy}
    & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{19} \\
    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{13} \\
    & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{9} \\
    & \multicolumn{1}{l}{Pattern Matching}
                                       & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{19} \\
    \hline
    \multirow{2}{*}{\textbf{Language Dependence}}
    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{37} \\
    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{16} \\
    \hline
    \multirow{3}{*}{\textbf{Analysis Type}}
    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{25} \\
    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{13} \\
    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{17} \\
    \hline
    \multirow{3}{*}{Detection Level}
    & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{8} \\
    \hline
    \multirow{2}{*}{Detection generality}
    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{40} \\
    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{11} \\
    \hline
    \multirow{4}{*}{Detected Pattern Types}
    & \multicolumn{1}{l}{Creational}  & \multicolumn{1}{l}{22} \\
    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{33} \\
    & \multicolumn{1}{l}{Behavior}    & \multicolumn{1}{l}{37} \\
    & \multicolumn{1}{l}{Other/Not Specified}
                                       & \multicolumn{1}{l}{12} \\
    \hline
    \multirow{6}{*}{Validation Method}
    & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{37} \\
    & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Survey}       & \multicolumn{1}{l}{0} \\
    & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{8}
   \end{tabular}
   \caption{Classification Results - Categories whose values represent disjoint sets are presented in bold}

  \end{figure}
\end{center}

@@

%\begin{center}
%\includegraphics[scale=0.75]{detection_strategy.png}
%\end{center}

@@

%\begin{center}
%\includegraphics[scale=0.75]{analysis_type.png}
%\end{center}

@@

%\begin{center}
%  \includegraphics[scale=0.65]{pattern_types.png}
%\end{center}

@@

%\begin{center}
%\includegraphics[scale=0.75]{language_generality.png}
%\end{center}

@@

%\begin{center}
%\includegraphics[scale=0.75]{detection_level.png}
%\end{center}

@@

Heričko and Beloglavec[355] presents a way of identifying
composite design pattern, not to be confused with the definition of the 
composite pattern defined by the GoF, here composite pattern corresponds to the
composition of atomic design pattern (the Model View Controler being an
example of a composite pattern).

@@

%\begin{center}
%\includegraphics[scale=0.75]{detection_generality.png}
%\end{center}

@@

Also, because most technique are language dependant, comparative studies are
often times limited to case study in one language.
Again, few articles try to present results taken from software in written in
different languages.
This is problematic because no common ground for comparison exists between
technique whose evaluation is done on software written in different languages.
Gueheneux and Antoniol[255] presented an extensive evaluation of DeMIMA on
five open source Java projects and 33 industrial component written in C++.
While the use of closed source component is in itself problematic, the
evaluation of their system on both Java and C++ programs is noteworthy.

%TODO: citation needed
Other articles, due to the work involved in manually identifying instances of
design pattern for evaluation, have simply choosen to compare their result to
the output of existing tools.
Even if some use multiple tools to cross check the identified pattern instances,
we believe such evaluation methods are flawed since we don't know how well
those tools perform due to the absence of a standard benchmark.
The existence of pattern repository like P-MARt should supersede those
validation technique.

@@

All these issues seem to indicate a lack of maturity of the field of design
pattern detection.
At least, more work is needed compare the different techniques.

>>>>

We decided to query only one database, Scopus \cite{c2}, that claims to be the
largest abstract and citation database of peer-reviewed literature.
It indexes the main Computer Science databases : Springer, IEEE, ACM and
others.
The main advantage of using Scopus is that it provides a functionality to
export the result of a search query on its database.
Some of those exported results would not have been easily obtainable on some
publishers search engines that do not provide an export functionality.
Consequently, Scopus was used as a mostly as a search and export portal over the
relevant publications, greatly reducing the effort needed to extract the
initial articles set.

From the two research questions we tried to maximize the number of publications
found on the subject.
It was decided to run our query only on the title, the abstract and the keywords of
each article. 
Our query was relatively simple,  "design pattern" and "detection" had to be present
in the searched part of an article.
To maximize the number of publications found, we considered variations of both part
of our query in the form of synonyms and words sharing the same root.
Therefore, we have extended our query to not only match "design pattern" but "design motif" as well. In the same vein, instead of only "detection" and its variations
"identification" and "recognition", we queried their contracted forms "detect*",
"ident*", and "recogni*".

@@

We have also limited our research to the field of computer science and
engineering.

@@

@@

\begin{enumerate}
  \item \textbf{Not a contribution in software engineering}: 
    This criterion was used to exclude articles not relevant to the domain and
    software engineering articles that are nothing more than mere use case
    reports.
  \item \textbf{Not a full conference or research paper}:
    This criterion was used to exclude small research papers
  \item \textbf{Not about software design patterns}:
    This criterion excludes articles where the main contribution is not about
    software design patterns,
    % TODO: We cannoct base our exclusion to DP defined by the GoF because we
    % have a class for other pattern type.
    % Limiting to software design patterns would be enough
  \item \textbf{The main contribution of the paper is not about a method of detecting design patterns}:
    This criterion was used to exclude benchmarks and other analysis whose main
    purposes are not a method of design pattern detection.
\end{enumerate}

The rejection criteria are ordered: an article that doesn't satisfy a specific
criteron cannot be rejected for a succeeding one.
Hence, the lowest applicable exclution criteron should always be the cause of
rejection.

@@

\subsection{Systematic map}
The systematic mapping

@@

\textit{Fig. 1} illustrates the flow of information at each phase of the study.

\subsection{Selection}

As per the systematic mapping study process, we started with a sizeable initial
article set, reducing its size at each phase as not relevant articles were rejected.

Our initial article set was made of 403 articles returned by the query on Scopus
database.

Of those articles, we found two duplicates that were immediately removed from
the set of articles to analyze, which brought down the number of articles for
screening to 401.

After having queried the database and removed the duplicates, we exported the
results found as a .csv file and proceeded to screening.

As we were three authors to work on the screening, we created three pairs
of evaluators and distributed the articles evenly between them.

The screening phase was done with the help of a spreadsheet where a column was
created for each evaluator.
Each evaluator was intructed to rate each article he's been assigned with a number
from 1 to 5, where 5 corresponds to the acceptation of the article and numbers below
to the applicable rejection criteron as defined in the previous section.
To prevent the rejection of relevant article, raters were instructed to accept
any article susceptible of being relevant with the afterthought that it could be
rejected after a complete reading.

Each article was rated according to the reading of its title and its abstract by
individual evaluator.

\begin{figure}
 \centering
  \begin{tabular}{ ccc }
   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
   \hline {}
   1 & 132 & 0.88 \\
   2 & 133 & 0.66 \\
   3 & 134 & 0.91 \\
 \end{tabular}
 \caption{Cohen's Kappa coefficients}
\end{figure}

For each article, we ensured that articles were rated consistently amongst the
evaluators.

Disagreement in the rating of article inside a pair were firstly dealt with a
reconsidaration of the rating of each individual according to the arguments of his opposing rater.
In the case of unresolved disagreement, we brought our case before a senior
researcher that published in the studied field who would instruct us over the final
decision.
If even he could settle de disagreement, the article was included to possibly be
excluded at a later point.

\subsubsection{Cohen's kappa coefficient}
We calculated inter-rater agreement Cohen's kappa coefficient over the
rejection and acceptation of each articles, which gaves us an average coefficient
of 0.82.
Individual results for each pair of evaluators is given in \textit{Fig. 2}
alongside the number of articles assigned to each one.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.450]{year_distribution.png}
  \caption{}
\end{figure}

\begin{figure}
  \centering
   \small
   \begin{tabular}{ lll }
    \bf Category & \bf Class & \bf \# of articles \\
    \hline
    \multirow{7}{*}{Detection Strategy}
    & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{19} \\
    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{13} \\
    & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{9} \\
    & \multicolumn{1}{l}{Pattern Matching}
                                       & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{19} \\
    \hline
    \multirow{2}{*}{\textbf{Language Dependence}}
    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{37} \\
    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{16} \\
    \hline
    \multirow{3}{*}{\textbf{Analysis Type}}
    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{25} \\
    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{13} \\
    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{17} \\
    \hline
    \multirow{3}{*}{Detection Level}
    & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{8} \\
    \hline
    \multirow{2}{*}{Detection generality}
    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{40} \\
    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{11} \\
    \hline
    \multirow{4}{*}{Detected Pattern Types}
    & \multicolumn{1}{l}{Creational}  & \multicolumn{1}{l}{22} \\
    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{33} \\
    & \multicolumn{1}{l}{Behavior}    & \multicolumn{1}{l}{37} \\
    & \multicolumn{1}{l}{Other/Not Specified}
                                       & \multicolumn{1}{l}{12} \\
    \hline
    \multirow{6}{*}{Validation Method}
    & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{37} \\
    & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Survey}       & \multicolumn{1}{l}{0} \\
    & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{8}
   \end{tabular}
   \caption{Classification Results - Categories whose values represent disjoint sets are presented in bold}

\end{figure}

@@

@@

@@

@@

@@

@@

Heričko and Beloglavec[355] presents a way of identifying
composite design pattern, not to be confused with the definition of the 
composite pattern defined by the GoF, here, composite pattern corresponds to the
composition of atomic design pattern (the Model View Controler pattern being an
example of a composite pattern).

@@

@@

Also, because most technique are language dependant, comparative studies are
often times limited to case study in one language.
Again, few articles try to present results taken from software written in
different languages.
This is problematic because no common ground for comparison exists between
technique whose evaluation is done on software written in different languages.
Gueheneux and Antoniol[255] presented an extensive evaluation of DeMIMA on
five open source Java projects and 33 industrial component written in C++.
While the use of closed source components is in itself problematic, the
evaluation of their system on both Java and C++ programs is noteworthy.

%TODO: citation needed
Other articles, due to the work involved in manually identifying instances of
design pattern for evaluation, have simply choosen to compare their result to
the output of existing tools.
Even if some use multiple tools to cross-check the identified pattern instances,
we believe such evaluation methods are flawed since we don't know how well
those tools perform due to the absence of a standard benchmark.
The existence of pattern repository like P-MARt should supersede those
validation techniques.

@@

All these issues seem to indicate a lack of maturity of the field of design
pattern detection.
At least, more work is necessary to compare the different techniques.
